---
title: "Developing Data Products Final Project"
author: "John Ferguson"
date: "4/21/2020"
output: ioslides_presentation
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = FALSE)
```

## Assignment

- Deploy the application on Rstudio's shiny server
- Share the application link by pasting it into the provided text box
- Share your server.R and ui.R code on github
- The application must include the following:
    1. Some form of input (widget: textbox, radio button, checkbox, ...)
    2. Some operation on the ui input in sever.R
    3. Some reactive output displayed as a result of server calculations
    4. You must also include enough documentation so that a novice user could use your application.

## Project Overview

### This project derives three models to perdict Horsepower for a car using the MTCARS data set

- The first model The first model is a simple model that predicts Horsepower based on MPG

- The second model is a model that predicts Horsepower based on MPG, where MPG is set at zero for all MPGs less than 20 MPG

- The third model is a model that predicts Horsepower based on MPG and Cylinders

## R Code for the models

```{r, echo=TRUE}
mtcars$mpgsp <- ifelse(mtcars$mpg - 20 > 0, mtcars$mpg - 20, 0)
model1 <- lm(hp ~ mpg, data = mtcars)
model2 <- lm(hp ~ mpgsp + mpg, data = mtcars)
model3 <- lm(hp ~ mpg + cyl, data = mtcars)

```


## Model Plots (Where Cylinders = 6)

```{r}
        mtcars$mpgsp <- ifelse(mtcars$mpg - 20 > 0, mtcars$mpg - 20, 0)
        model1 <- lm(hp ~ mpg, data = mtcars)
        model2 <- lm(hp ~ mpgsp + mpg, data = mtcars)
        model3 <- lm(hp ~ mpg + cyl, data = mtcars)
        plot(mtcars$mpg, mtcars$hp, xlab = "Miles Per Gallon",
             ylab = "Horsepower", bty = "n", pch = 16,
             xlim = c(10, 35), ylim = c(50, 350))
        abline(model1, col = "red", lwd = 2)
        model2lines <- predict(model2, newdata = data.frame(
                mpg = 10:35, mpgsp = ifelse(10:35 - 20 > 0, 10:35 - 20, 0)
            ))
        lines(10:35, model2lines, col = "blue", lwd = 2)
        model3lines <- predict(model3, newdata = data.frame(
                mpg = 10:35, cyl = 6)
            )
            lines(10:35, model3lines, col = "green", lwd = 2)

       legend(25, 250, c("Model 1 Prediction", "Model 2 Prediction","Model 3 Prediction"), pch = 16,
               col = c("red", "blue","green"), bty = "n", cex = 1.2)
```


